### 2021-07-12 src/paper/results/rapid_tests_statistics.tex
Polish rapid test statistics section.

\subsection{Simulated Rapid Test Statistics}
\label{subsec:results_rapid_test_statistics}

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case, which can be seen from the
number of
false negative tests. At its peak at the beginning of May, there are more than 80 false
negative rapid tests per million inhabitants per day. While this number might sound low
in isolation, it becomes quite large when set in context: We estimate that at May first
there are about 200 detected new infections per million inhabitants and day and roughly
the same number of undetected cases. Thus there are only 400 per million inhabitants
who could test falsely negative to begin with and not all of them will make a rapid
test. This shows clearly that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are positive. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.

>>>>

\subsection{Simulated Rapid Tests}
\label{subsec:results_rapid_test_statistics}

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case, which can be seen from the
number of
false negative tests. At its peak at the beginning of May, there are more than 80 false
negative rapid tests per million inhabitants per day. While this number might sound low
in isolation, it becomes quite large when set in context: We estimate that at at the
the same time only 200 cases per million are detected by rapid tests. This means that
even at the time where discovery of cases via rapid tests is at its peak, almost
30\% of of people who are infected and make a test are not discovered by the test.

This shows clearly that the large effect of rapid tests on the infection dynamic
is not driven by unrealistic assumptions about their sensitivity but rather by the
fact that there was a very large number of infected individuals who did not know they
are positive. Detecting and isolating some of them is enough to slow down the
overall infection dynamic.
